\texttt{\df} -- \\ modifying drafted figures\footnote{ For further information about the code visit \href{https://github.com/LukasCBossert/draftfigure}{https://github.com/LukasCBossert/draftfigure} Comments and criticisms are welcome.}

### 2017-05-07 draftfigure-preamble.tex
done version 0.1
cleaning - changing papersize

@@

\usepackage{hyperxmp}
\usepackage{hyperref}
\hypersetup{					% setup the hyperref-package options
  unicode       = true,
	pdftitle      = {draftfigure},	% 	- title (PDF meta)
	pdfsubject    = {},% 	- subject (PDF meta)
	pdfauthor      = {Lukas C. Bossert},	% 	- author (PDF meta)
	pdfauthortitle = {},
	pdfcopyright   = {This work may be distributed and/or modified under the
        conditions of the LaTeX Project Public License, either version 1.3
        of this license or (at your option) any later version.},
	pdfhighlight   = /N,
	pdfdisplaydoctitle = true,
	pdfdate        = {\the\year-\the\month-\the\day}
	pdflang        = {en},
	pdfcaptionwriter = {Lukas C. Bossert},
	pdfkeywords    = {},
	pdfproducer={LuaLaTeX},
	pdflicenseurl  = {http://www.latex-project.org/lppl.txt},
	plainpages     = false,			% 	- 
  colorlinks     = true, %Colours links instead of ugly boxes
  urlcolor       = codeblue, %Colour for external hyperlinks
  linkcolor      = codeblue, %Colour of internal links
  citecolor      = black, %Colour of citations
  linktoc        = page,
  pdfborder      = {0 0 0},			% 	-
	breaklinks     = true,			% 	- allow line break inside links
	bookmarksnumbered  = true,		%
	bookmarksopenlevel = 4,
	bookmarksopen  = true,		%
	final          = true
}
\usepackage{bookmark}

% \crefformat{lstlisting}{#2example\ #1#3}
% \Crefformat{lstlisting}{#2Example #1#3}
% \crefmultiformat{lstlisting}{#2examples #1#3}{; #2#1#3}{; #2#1#3}{; #2#1#3}
% \Crefmultiformat{lstlisting}{#2Examples #1#3}{; #2#1#3}{; #2#1#3}{; #2#1#3}
% \Crefrangeformat{lstlisting}{#3Examples #1#4--#5#2#6}
% \crefrangeformat{lstlisting}{#3examples #1#4--#5#2#6}

>>>>

\newlength{\ratio}
\newlength{\wrapfiguremargin}

\setlength{\ratio}{2cm}
\usepackage{lscape}%landscape-Modus
\usepackage[					% page layout modifications
	paper=a4paper,					% 	- use A4 paper size
%    head=.5\ratio,
	foot=.25\ratio,
	left=2\ratio,					% 	- total body: left margin (odd pages)
	top=1.5\ratio,						% 	- total body: top margin
	right=2\ratio,					% 	- total body: right margin (odd pages)
	bottom=\ratio,					% 	- total body: bottom margin
%	marginpar=3.5cm,			% 	- width for side note
	marginparwidth=1.5\ratio,			% 	- width for side note
	marginparsep=.25\ratio,				% 	- space between notes and body text (content)
]{geometry}

@@

%------ changelog
\usepackage{xparse,tabularx}

\ExplSyntaxOn

\NewDocumentCommand{\AddRevision}{mmm}
 {
  \draftfigure_revision_add:nnn { #1 } { #2 } { #3 }
 }
\NewDocumentCommand{\PrintRevisions}{}
 {
  \begin{center}
  \cs_set_eq:NN \__draftfigure_revision_do:nnn \draftfigure_revision_date:nnn
  \seq_set_eq:NN \l__draftfigure_revision_temp_seq \g_draftfigure_revision_list_seq
  \seq_sort:Nn \l__draftfigure_revision_temp_seq
   {
    \int_compare:nNnTF
     { ##1 } > { ##2 }
     { \sort_return_same: }
     { \sort_return_swapped: }
   }
  \cs_set_eq:NN \__draftfigure_revision_do:nnn \draftfigure_revision_entry:nnn
  \int_gset:Nn \g__draftfigure_revision_entry_int { \seq_count:N \l__draftfigure_revision_temp_seq }
  \tl_clear:N \l__draftfigure_revision_tablebody_tl
  \seq_map_inline:Nn \l__draftfigure_revision_temp_seq
   {
    \int_gdecr:N \g__draftfigure_revision_entry_int
    \tl_put_right:Nf \l__draftfigure_revision_tablebody_tl
     { \int_to_arabic:n { \g__draftfigure_revision_entry_int } ##1 }
   }
  \begin{tabularx}{\textwidth}{llXr}
  \multicolumn{4}{l}{Revisions} \\
  \hline
  \tl_use:N \l__draftfigure_revision_tablebody_tl
  \hline
  \end{tabularx}
  \end{center}
 }

\seq_new:N \g_draftfigure_revision_list_seq
\seq_new:N \l__draftfigure_revision_temp_seq
\int_new:N \g__draftfigure_revision_entry_int
\tl_new:N \l__draftfigure_revision_tablebody_tl
\cs_generate_variant:Nn \tl_put_right:Nn { Nf }

\cs_new_protected:Nn \draftfigure_revision_add:nnn
 {
  \seq_gput_right:Nn \g_draftfigure_revision_list_seq
   {
    \__draftfigure_revision_do:nnn { #1 } { #2 } { #3 }
   }
 }

\cs_new:Nn \draftfigure_revision_entry:nnn
 {
   & #1 & #2 & #3 \\
 }

\cs_new:Nn \draftfigure_revision_date:nnn
 {
  \__draftfigure_revision_make_date:w #1 \q_stop
 }
\cs_new:Npn \__draftfigure_revision_make_date:w #1-#2-#3 \q_stop
 {
  #1#2#3
 }
\ExplSyntaxOff
%--------

\usepackage{hyperxmp}
\usepackage{hyperref}
\hypersetup{					% setup the hyperref-package options
  unicode       = true,
	pdftitle      = {draftfigure},	% 	- title (PDF meta)
	pdfsubject    = {},% 	- subject (PDF meta)
	pdfauthor      = {Lukas C. Bossert},	% 	- author (PDF meta)
	pdfauthortitle = {},
	pdfcopyright   = {This work may be distributed and/or modified under the
        conditions of the LaTeX Project Public License, either version 1.3
        of this license or (at your option) any later version.},
	pdfhighlight   = /N,
	pdfdisplaydoctitle = true,
	pdfdate        = {\the\year-\the\month-\the\day}
	pdflang        = {en},
	pdfcaptionwriter = {Lukas C. Bossert},
	pdfkeywords    = {},
	pdfproducer={LuaLaTeX},
	pdflicenseurl  = {http://www.latex-project.org/lppl.txt},
	plainpages     = false,			% 	- 
  colorlinks     = true, %Colours links instead of ugly boxes
  urlcolor       = codeblue, %Colour for external hyperlinks
  linkcolor      = codeblue, %Colour of internal links
  citecolor      = black, %Colour of citations
  linktoc        = page,
  pdfborder      = {0 0 0},			% 	-
	breaklinks     = true,			% 	- allow line break inside links
	bookmarksnumbered  = true,		%
	bookmarksopenlevel = 4,
	bookmarksopen  = true,		%
	final          = true
}
\usepackage{bookmark}
\usepackage{cleveref}

\crefformat{lstlisting}{#2example\ #1#3}
\Crefformat{lstlisting}{#2Example #1#3}
\crefmultiformat{lstlisting}{#2examples #1#3}{; #2#1#3}{; #2#1#3}{; #2#1#3}
\Crefmultiformat{lstlisting}{#2Examples #1#3}{; #2#1#3}{; #2#1#3}{; #2#1#3}
\Crefrangeformat{lstlisting}{#3Examples #1#4--#5#2#6}
\crefrangeformat{lstlisting}{#3examples #1#4--#5#2#6}
